\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2025-02-23 Manuscript/manuscript.tex
comments on section 2 and 3

@@

To investigate whether RTs at the 2022 World Championships
were significantly different from other competitions, we
used data from male athletes in the 110-meter hurdles and 100-meter
dash, and female athletes in the 100-meter hurdles and 100-meter dash,
provided they competed in the 2022 World Championships and at least
one other competition (2022 national championships, 2019 World
Championships, or 2023 World Championships).  We excluded data from
200-meter dashes and longer events, as their RTs were found
to be significantly different. Negative RTs were excluded from the analysis,
while positive disqualified RTs were included due to their low frequency and not
being obvious outliers.

@@

@@

To compare RTs at the 2022 World Championships with those
recorded in the 2019 and 2023 World Championships, we prepared datasets
including RTs from athletes who competed in the 2022 World
Championships and at least one of the 2019 or 2023 World Championships.
Specifically, we identified athletes who participated in both the 2019
and 2022 World Championships, as well as those who participated in both
the 2022 and 2023 World Championships. In the 2019-2022 comparison,
RTs from 2022 were treated as the `treatment' group, with
2019 serving as the `control' group. Similarly, in the 2022-2023
comparison, RTs from 2022 were treated as the `treatment'
group, with 2023 serving as the `control' group. This structure allowed
us to prepare datasets suitable for examining RTs of athletes
who competed across multiple World Championships.

@@

>>>>

\jy{State the hypotheses here before diving into data/methods/results.}

@@

\jy{This two paragraphs are repetitive. Condense.}
To investigate whether RTs at the 2022 World Championships
were significantly different from other competitions, we
used data from male athletes in the 110-meter hurdles and 100-meter
dash, and female athletes in the 100-meter hurdles and 100-meter dash,
provided they competed in the 2022 World Championships and at least
one other competition (2022 national championships, 2019 World
Championships, or 2023 World Championships).  We excluded data from
200-meter dashes and longer events, as their RTs were found
to be significantly different. Negative RTs were excluded from the analysis,
while positive disqualified RTs were included due to their low frequency and not
being obvious outliers.

@@

\jy{Opening sentence not accurate. This is the data to test the first
  hypothesis: national versus World Championship 2022.}

@@

\jy{Improve the topic sentence: this data is for the second
  hypothesis: 2019 vs 2022; 2023 vs 2022.}
To compare RTs at the 2022 World Championships with those
recorded in the 2019 and 2023 World Championships, we prepared datasets
including RTs from athletes who competed in the 2022 World
Championships and at least one of the 2019 or 2023 World Championships.
Specifically, we identified athletes who participated in both the 2019
and 2022 World Championships, as well as those who participated in both
the 2022 and 2023 World Championships. In the 2019-2022 comparison,
RTs from 2022 were treated as the `treatment' group, with
2019 serving as the `control' group. Similarly, in the 2022-2023
comparison, RTs from 2022 were treated as the `treatment'
group, with 2023 serving as the `control' group. This structure allowed
us to prepare datasets suitable for examining RTs of athletes
who competed across multiple World Championships.

@@

\jy{write a quick overview paragraph here.}
